Appendix A - Alternative DSDM formulations

### 2019-10-25 manuscript/appendix_a.Rmd
starrt adding IPM code

>>>>

\begin{align}
a
\end{align}

- `matrix_dim`: a positive integer giving the dimension of the matrix used to integrate the IPM kernel
- `X_off_size`: a $N$x$K_{off_size}$ design matrix for the offspring size environmental sub-model
- `X_surv`: a $N$x$K_{surv}$ design matrix for the survival environmental sub-models
- `X_growth`: a $N$x$K_{grow}$ design matrix for the growth environmental sub-model
- `X_seedheads`: a $N$x$K_{seedhead}$ design matrix for the seedhead environmental sub-model
- `beta_env_off_size`: a length $K_{off_size}$ vector of environmental regression coefficients for offspring size
- `beta_env_surv_seedling`: a length $K_{surv}$ vector of environmental regression coefficients for logit-seedling-survival
- `beta_env_surv_adult`: a length $K_{surv}$ vector of environmental regression coefficients for logit-adult-survival
- `beta_env_growth`: a length $K_{grow}$ vector of environmental regression coefficients for growth
- `beta_env_seedheads`: a length $K_{seedhead}$ vector of environmental regression coefficients for log-seadhead production
- `beta_size_surv_seedling`: ?
- `beta_size_surv_adult`: ?
- `beta_size_grow`: ?
- `beta_size_flower`: ?
- `beta_germ`: ?
- `beta_seeds`: ?

```{r ipms}
min_size <- 0
max_size <- 5
bounds <- min_size + (0:matrix_dim) * (max_size - min_size) / matrix_dim
sizes <- 0.5 * (bounds[-(matrix_dim + 1)] + bounds[-1])
bin_width <- sizes[2] - sizes[1]

# environmental components of sub models
off_size <- X_off_size %*% beta_env_off_size
growth <- X_growth %*% beta_env_growth
env_surv_seedling <- X_surv %*% beta_env_surv_seedling
env_surv_adult <- X_surv %*% beta_env_surv_adult
env_seedheads <- X_seedheads %*% beta_env_seedheads

# size components of submodels
flower <- ilogit(sizes * beta_size_flower)
size_surv_seedling <- sizes * beta_size_surv_seedling
size_surv_adult <- sizes * beta_size_surv_adult
size_seedheads <- sizes * beta_size_seedheads

# combined size and environmental effects
seedheads <- exp(kronecker(size_seedheads, env_seedheads))
surv_seedling <- ilogit(kronecker(size_surv_seedling, env_surv_seedling))
surv_adult <- ilogit(kronecker(size_surv_adult, env_surv_adult))

germination <- ilogit(beta_germ)
seeds <- exp(beta_seeds)

# kernelise growth and offspring size
growth_density <- distribution_kernel(grow, grow_sd, sizes, bin_width)
off_size_density <- distribution_kernel(off_size, off_size_sd, sizes, bin_width)

# combine adult and seedling survival rates into one
survival <- interpolate_survival(surv_adult, surv_seedling, sizes)

# apply survival to growth density
P <- sweep_3(growth_density, survival, FUN = "*")

# apply recruitment rate to offspring size density
recruits <- flower * seedheads * seeds * germ
F <- sweep_3(offspring_size_density, recruits, FUN = "*")

A <- P + F
```
